### 2024-06-12 conteudo/background/linux.tex
Add another part of the process

TEXT ABOUT LINUX NUMBER SCOPE ETC.

The Linux project is organized as a set of subsystem such as process scheduler, memory management, 
device driver infrastruture, networking and filesystems \citep{melissa}.
Each subsystem usually have a maintainer or a group of maintainers, which are people responsible 
for managing and accepting contributions into the subsystem they care of it \citep{melissa}.

@@

TALK ABOUT HOW THE TOOL ENABLE A NEW WAY TO START CONTRITUTING TO THE KERNEL

AMD Display Driver is a linux's subsystem responsible for the management of AMD GPU's. This subsystem have a problem 
with code clone duplication acknowledged by the subsystem's maintainters. For this reason, we selected this
subsystem as the primary focus for our empirical analysis in our research.

>>>>

The Linux kernel is monolithic organized as a set of subsystem such as process scheduler, memory management, 
device driver infrastruture, networking and filesystems \citep{melissa}.
Each subsystem usually have a maintainer or a group of maintainers, which are people responsible 
for managing and accepting contributions into the subsystem they care of \citep{melissa}.

@@

AMD Display Driver is a linux's subsystem responsible for the management of AMD GPU's. This subsystem have a problem 
with code clone duplication, which are acknowledged by the subsystem's maintainters. For this reason, we selected this
subsystem as the primary focus for refactoring the detected code clone duplication by our tool.
(MAYBE CHANGE TO: For this reason, we selected this subsystem as the primary focus for our empirical analysis in our research).
